The Effects of Varying Depth in Cosmic Shear Surveys

### 2019-07-30 paperdraft.tex
removed cosebis of reference function

To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10), once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then for the correlation functions that have been modified to account for a varying depth. We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}. It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.\todo{add reference in the figure as soon as marika's paper is on arxiv}

>>>>

To estimate the B-modes created by this effect, we have extracted the \emph{Complete Orthogonal Sets of E- and B-Mode Integrals} (COSEBIS, compare S10)
%, once of a reference set of correlation functions, to estimate numerical inaccuracies,\footnote{For a reference correlation function the B-Modes should be consistent with zero.} and then 
 for the correlation functions $\xi_\pm^{\rm{obs}}$ that have been modified under the semi-analytic model. We report a consistent B-mode behaviour across all redshift-bins, which can be seen in Figure \ref{fig:bmodes_cosebi}. It should be noted that the difference in E-modes is as large as the B-modes, which suggests that any significant change in the cosmological parameters due to a varying depth will also yield the significant detection of B-modes.\todo{add reference in the figure as soon as marika's paper is on arxiv}
